A Documentary History of \\ the Nock Combinator Calculus

### 2025-08-12 mss.tex
Post

Axiomatic operator \texttt{*} tar\footnote{We refer to Nock axiomatic operators via their modern aural \textsc{ascii} pronunciations.  While these evolved over time (to wit, \texttt{\textasciicircum} ``hat'' became ``ket''), to attempt to synchronize pronunciation with the era of a Nock release is a fool's errand.} is identified as a \texttt{GOTO}.\footnote{One can see the influence of this version's naming scheme on Atman's Ax, pp.~XX–XX herein.}

>>>>

Axiomatic operator \texttt{*} tar\footnote{We refer to Nock axiomatic operators via their modern aural \textsc{ascii} pronunciations.  While these evolved over time (to wit, \texttt{\textasciicircum} ``hat'' became ``ket''), to attempt to synchronize pronunciation with the era of a Nock release is a fool's errand.} is identified as a \texttt{GOTO}.\footnote{One can see the influence of this version's naming scheme on \patp{barpub-tarber}'s Ax, pp.~189–226 herein.}
